---
title: 'DDP Project: Shiny Apps for Data Exploration'
author: "cyanophyta"
date: "02/09/2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Goal of the application

- While exploring a dataset we need to study basic plots of various variables of a dataset. 
- We attempt to make this work easier by using a Shiny Apps application here. 
- Dataset considered here is faithfuld from ggplot2 package.

```{r warning=FALSE, echo = TRUE}
library(ggplot2, warn.conflicts = FALSE, quietly = TRUE)
data("faithfuld")
dim(faithfuld)
str(faithfuld)
```

## App features
Using this app, user can

* study Histogram, Line Graph or Box-and-whisker Plot of any variable in the dataset
* change color of the graph, if needed
* in case of histogram, change number of intervals (bins) to be used in the graph
* study summary data for the selected variable, displayed in the following format:
```{r echo=TRUE}
  summat <- as.matrix(summary(faithfuld$waiting))
  rownames(summat) <- c("Minimum", "1st quartile", "Median", "Mean", "3rd quartile", "Maximum")
  colnames(summat) <- "Summary"
  summat
```

## Sample plot types for variable 'waiting'

User selects one of the variables of the dataset in the Shiny app. Based on this selection, and type of graph/color, one of the available graph is displayed by the app.
```{r echo=FALSE}
color <- "gray"
par(mfrow = c(3, 1))
x <- faithfuld$waiting
bins <- seq(min(x), max(x), length.out = 20 + 1)
hist(x, 
     breaks = bins, 
     col = color, 
     border = 'white', 
     main = paste("Histogram of ", "Waiting time"), 
     xlab = "Waiting time")   
plot(x, 
     type = "l", 
     col = color, 
     main = paste("LIne Graph of ", "Waiting time"), 
     xlab = "Index", 
     ylab = "Waiting time")
boxplot(x, 
        col = color, 
        main = paste("Box and Whisket Plot of ", "Waiting time"),
        xlab = "Waiting time")
```

## Possible future enhancements

- add more tuning parameters for the graphs
- add a tab to select any of the two variables and show scatter plot
- add a tab, where user can select multiple variables and then display pairwise scatter plots

